Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-09 mtjournal.tex
no date included, a single reference now in place, dropped inline bibitems

\begin{document}                                                                                   
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting improvements to {HTER} with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
\date{May 10, 2009}

@@

\begin{itemize}
\item evaluation [esp. automatic evaluation]
\item popular current
  measures BLEU, TER

@@

\section{References in the THEBIBLIOGRAPHY Environment}
The first reference in the list below has the key \{BrownAndBurton\}.
Together with the bibitem option $\backslash$citeauthoryear\{Brown and
Burton\}\{1978\} the follwing cross-references can be used:\\
$\backslash$cite\{BrownAndBurton\} produces: \cite{BrownAndBurton}\\
$\backslash$shortcite\{BrownAndBurton\}  produces: \shortcite{BrownAndBurton}\\  
$\backslash$citeauthor\{BrownAndBurton\}  produces: \citeauthor{BrownAndBurton}\\  
$\backslash$citeyear\{BrownAndBurton\}  produces: \citeyear{BrownAndBurton}\\

@@

And this is my Appendix.

\acknowledgements
And this is an acknowledgements section with a heading that was produced by the
$\backslash$acknowledgements command. Thank you all for helping me writing this
\LaTeX\ sample file.

% The endnotes section will be placed here.

\theendnotes

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Brown and Burton}{1978}]{BrownAndBurton}
J.~S. Brown and R.~R. Burton.
\newblock {Diagnostic Models for Procedural Bugs in Basic Mathematical Skills}.
\newblock {\em Cognitive Science}, 2(2):155--192, 1978.

\bibitem[\protect\citeauthoryear{Buchanan}{1984}]{BuchananRBES}
Bruce~G. Buchanan and Edward~H. Shortliffe.
\newblock {\em Rule-Based Expert Systems: The MYCIN Experiments of the Stanford
  Heuristic Programming Project}.
\newblock Addison-Wesley Publishing Company, 1984.

\bibitem[\protect\citeauthoryear{Bunt}{1990}]{Bunt}
H.~C. Bunt.
\newblock {Modular Incremental Modelling of Belief and Intention}.
\newblock In {\em Proceedings of the Second International Workshop on User
  Modeling}, 1990.

\bibitem[\protect\citeauthoryear{Cahour}{1990}]{Cahour-90-Montreal}
B\'eatrice Cahour.
\newblock {Competence Modelling in Consultation Dialogs}.
\newblock In L.~Berlinguet and D.~Berthelette, editors, {\em Proceedings of the
  International Congress, Work With Dispay Units' 89}, Montreal, Canada,
  September 1990. North Holland, Amsterdam.

\bibitem[\protect\citeauthoryear{Cahour}{1988}]{Cahour-thesis}
B\'eatrice Cahour.
\newblock {\em {La Mod\'elisation de l'Interlocuteur: Elaboration du Mod\`ele
  et Effets au Cours de Dialogues de Consultation}}.
\newblock PhD thesis, Universit\'e Paris 8, France, 1991.
\newblock Cognitive psychology PhD.

\bibitem[\protect\citeauthoryear{Carberry}{1988}]{CarberryCL88}
Sandra~M. Carberry.
\newblock {Modeling the User's Plans and Goals}.
\newblock {\em Computational Linguistics}, 14(3):23--37, September 1988.

\bibitem[\protect\citeauthoryear{Carbonell}{1970}]{CarbonellScholar}
J.~R. Carbonell.
\newblock {AI in CAI: An Artificial Intelligence Approach to Computer-Aided
  Instruction}.
\newblock {\em IEEE Transactions on Man-Machine Systems}, 11:190--202, 1970.

\bibitem[\protect\citeauthoryear{Carr and Goldstein}{1977}]{Carr-Goldstein}
B.~Carr and I.~Goldstein.
\newblock {Overlays: A Theory of Modelling for Computed Aided Instruction}.
\newblock AI Memo 406, 1977.

\bibitem[\protect\citeauthoryear{Cawsey}{(in press)}]{CawseyIJMMS}
Alison Cawsey.
\newblock {Planning Interactive Explanations}.
\newblock {\em International Journal of Man-Machine Studies}, in press.

\bibitem[\protect\citeauthoryear{Chandrasekaran and Swartout}{1991}]{chandra-swartout}
B.~Chandrasekaran and William Swartout.
\newblock {Explanations in Knowledge Systems: The Role of Explicit
  Representation of Design Knowledge}.
\newblock {\em IEEE Expert}, 6(3):47--50, June 1991.

\bibitem[\protect\citeauthoryear{Chappel and Cahour}{1991}]{MMI2-d3}
Helen Chappel and B\'eatrice Cahour.
\newblock {User Modeling for Multi-Modal Co-Operative Dialogue with KBS}.
\newblock Deliverable D3, Esprit Project P2474, 1991.

\bibitem[\protect\citeauthoryear{Chin}{1987}]{ChinThesis}
David~N. Chin.
\newblock {\em Intelligent Agents as a Basis for Natural Language Interfaces}.
\newblock PhD thesis, University of California at Berkeley, 1987.

\bibitem[\protect\citeauthoryear{Chin}{1989}]{Chin88-book}
David~N. Chin.
\newblock {KNOME}: {M}odeling {W}hat the {U}ser {K}nows in {UC}.
\newblock In Alfred Kobsa and Wolfgang Wahlster, editors, {\em User Models in
  Dialog Systems}. Springer-Verlag, Symbolic Computation Series, Berlin
  Heidelberg New York Tokyo, 1989.

\bibitem[\protect\citeauthoryear{Cohen and Jones}{1989}]{Cohen-Jones88-book}
Robin Cohen and Marlene Jones.
\newblock {Incorporating User Models into Expert Systems for Educational
  Diagnosis}.
\newblock In Alfred Kobsa and Wolfgang Wahlster, editors, {\em User Models in
  Dialog Systems}, pages 35 -- 51. Springer-Verlag, Symbolic Computation
  Series, Berlin Heidelberg New York Tokyo, 1989.

\bibitem[\protect\citeauthoryear{Falzon}{1987}]{Falzon87}
Pierre Falzon.
\newblock {Les Dialogues de Diagnostic: L'\'evaluation des Connaissances de
  l'Interlocuteur}.
\newblock Technical Report 747, INRIA, Rocquencourt, France, 1987.

\bibitem[\protect\citeauthoryear{Finin et al.}{1986}]{FininJoshiWebber}
Timothy~W. Finin, Aravind~K. Joshi, and Bonnie~Lynn Webber.
\newblock {Natural Language Interactions with Artificial Experts}.
\newblock {\em Proceedings of the IEEE}, 74(7), July 1986.

\end{thebibliography}
\end{article}
\end{document}

>>>>

\begin{document}                                                                                   
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting improvements to {HTER} with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

@@

\begin{itemize}
\item evaluation [esp. automatic evaluation]
\item popular current
  measures BLEU \cite{papineni02bleu}, TER

@@

@@

[don't think we want an appendix]

\acknowledgements

[grant numbers for the DARPA/GALE grants here]

% The endnotes section will be placed here.  But I don't think we have any

% \theendnotes

\bibliographystyle{klunamed}
\bibliography{edpm-paper}

\end{article}
\end{document}
